\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

We would like to express our sincere gratitude to all those who have contributed to the successful completion of this project.

First and foremost, we extend our heartfelt thanks to our project guide, Dr. [Guide Name], Professor in the Department of Information Technology, for his invaluable guidance, continuous support, and encouragement throughout the duration of this project. His expertise in computer vision and educational technology provided us with the necessary direction to navigate through the complexities of this research.

We are deeply grateful to our external guide, Dr. [External Guide Name], for sharing their industry experience and providing practical insights that enhanced the real-world applicability of our OMR Checker system.

We would like to thank the Department of Information Technology at Fr. Conceicao Rodrigues Institute of Technology for providing us with the necessary resources, infrastructure, and academic environment to pursue this project.

Special thanks to the open-source community, particularly the developers of OpenCV, NumPy, pandas, and other libraries that formed the foundation of our implementation. The extensive documentation and community support made the development process significantly smoother.

We acknowledge the contributions of Adrian Rosebrock from PyImageSearch, whose comprehensive tutorials on computer vision and OpenCV provided invaluable learning resources. We also thank Harrison Kinsley (sentdex) for his educational content on Python programming and machine learning.

Our sincere appreciation goes to Satya Mallick from LearnOpenCV for his resourceful blog posts and tutorials that enhanced our understanding of image processing techniques.

We are grateful to the Technothlon organization for testing our system at a large scale, which provided valuable feedback for improving the robustness and reliability of our implementation.

We would like to thank our fellow students and colleagues who provided feedback during the testing phase and helped us identify areas for improvement.

Finally, we extend our gratitude to our families and friends for their unwavering support, patience, and encouragement throughout this journey.

This project would not have been possible without the collective effort and support of all the individuals and organizations mentioned above.